Distribution-oblivious Programming with Dish

### 2019-09-22 pldi/draft.tex
Notes on POSIX file types

@@

\heading{Composition}
Composition

>>>>

At a high level, POSIX defines several file types:
(-) regular files, storing lines of text or binary data,
(d) directories, grouping together multiple other files,
(l) symbolic links, pointing to other files,
(p) named pipes or FIFOs, communication primitives that can be named and manipulated like files,
(s) domain sockets or DSes, full-duplex communication primitives that support passing file descriptors, and
(b or c) special files, interfaces to device drivers or low-level abstractions, presented as ordinary files.

Most of these identifiers are manipulated by file-system commands---\eg \ttt{mkdir} for directories and \ttt{mkfifo} for FIFOs.
FIFOs and DSes look like files but are streams.

Special files are particularly interesting because they are resolved to OS structures.
One set is pseudo-devices---device files that simply;
For example /dev/urandom returns a stream of random characters and /dev/null accepts and discards all input written to it.
Another set is proc filesystem (procfs), a special filesystem in Unix-like operating systems that presents information about processes and other system information.
For example, /proc/PID/cmdline contains command that originally started the process and /proc/PID/cwd contains a symlink to the current working directory of the process.

sysfs is a pseudo file system provided by the Linux kernel that exports information about various kernel subsystems, hardware devices, and

/modules, one of the most important files in /proc, containing a list of the kernel modules currently loaded . It gives some indication (not always entirely correct) of dependencies.
/cpuinfo

symbolic links, FIFO specials, 
device files
block special, character special, 
and domain sockets.

There are 3 standard streams (stdin, stdout, stderr) created automatically for most Unix programs.
These correspond to \ttt{/dev/fd/0}.
% These streams are created by the C library (glibc) at the start of program execution,
and new streams can be created to connect to files, sockets, pipes,

@@

\heading{Composition}
anonymous pipes

Composition
